\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amssymb}

\geometry{margin=1in}
\definecolor{accent}{HTML}{7896FF}
\definecolor{statusgray}{HTML}{666666}

\title{\Huge \textbf{\textcolor{accent}{Project Lume}}}
\author{Zero-Config AI-Driven LaTeX IDE}
\date{\today}

\begin{document}

\maketitle

\centerline{\textcolor{statusgray}{\textbf{Status}: Beta $|$ \textbf{Core}: Rust (Tauri / Tectonic) $|$ \textbf{UX}: Liquid Glass (React 19)}}

\vspace{1em}

\begin{abstract}
\textbf{Lume} (Latin for \textit{light/illumination}) is a next-generation LaTeX environment designed to end the nightmare of environmental configuration. By bridging a self-contained Tectonic compiler with an agentic AI core, Lume allows researchers, students, and writers to focus on creation rather than troubleshooting.
\end{abstract}

\section{The Vision}
\begin{itemize}
    \item \textbf{End Environment Hell}: Integrated Tectonic engine for ``compile-on-demand'' packages. No multi-gigabyte TeX Live installation required.
    \item \textbf{AI-First Workflow}: Built-in Lume Copilot for generating complex tables, formulas, and document structures via natural language.
    \item \textbf{Premium Aesthetics}: A ``Liquid Glass'' UI inspired by modern macOS design, featuring deep translucency and smooth transitions.
    \item \textbf{Native Performance}: Built with Rust for a minimal memory footprint and blistering fast compilation.
\end{itemize}

\section{Features \& Progress}

\subsection{Completed (Implemented)}
\begin{enumerate}[label=\checkmark]
    \item \textbf{Phase 1: The Forge}: Tauri + Tectonic Rust integration.
    \item \textbf{Phase 2: The Canvas}: CodeMirror 6 Editor and multi-page previewer.
    \item \textbf{Phase 3: The Soul}: Multi-model AI completion bridge (OpenAI, Claude, Gemini).
    \item \textbf{Phase 4: Advanced IDE Features}: VS Code-style Sidebar, multi-file support, and native PDF exporting.
\end{enumerate}

\subsection{In Progress / Planned}
\begin{itemize}[label=$\square$]
    \item Persistent AI Chat Sidebar.
    \item Multi-Provider Settings Page for API keys.
    \item Floating Document Structure (Section Jump).
    \item Dark/Light Mode Synchronization.
\end{itemize}

\section{Supported Platforms}
Lume is built on \textbf{Tauri 2.0}, ensuring native speed across major operating systems:
\begin{itemize}
    \item \textbf{macOS}: Fully optimized (Apple Silicon \& Intel).
    \item \textbf{Windows}: Windows 10/11 supported.
    \item \textbf{Linux}: Major distributions supported via AppImage/Deb.
\end{itemize}

\section{Tech Stack}
\begin{itemize}
    \item \textbf{Frontend}: React 19, Vite, Tailwind 4, CodeMirror 6.
    \item \textbf{Backend}: Rust, Tauri 2.0 (FS, Dialog, Shell plugins).
    \item \textbf{Compiler}: Tectonic (Native Rust sidecar).
    \item \textbf{PDF Engine}: PDF.js (WebWorker implementation).
\end{itemize}

\section{Getting Started}
\subsection{Development}
\begin{enumerate}
    \item \texttt{pnpm install}
    \item \texttt{pnpm tauri dev}
\end{enumerate}

\subsection{Build \& Deployment}
To generate a production-ready standalone installer:
\begin{itemize}
    \item Run: \texttt{pnpm tauri build}
    \item \textbf{macOS}: Output found in \texttt{target/release/bundle/dmg/}.
    \item \textbf{Windows/Linux}: Output found in respective bundle folders.
\end{itemize}

\vspace{2em}
\centerline{\textit{Focus on your content. Let Lume handle the rest.}}

\end{document}
